The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-02-07 paper.tex
About to start addressing Chris comments towards the end of ESO time 2017

\documentclass[a4paper,fleqn,usenatbib]{mn2e}

\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=Violet}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}   % Including figure files
\graphicspath{{Users/}{owenturner/}{Documents/}{PhD/}{KMOS/}{paper_1/}{Figures/}}
\usepackage{amsmath}    % Advanced maths commands
\usepackage{amssymb}    % Extra maths symbols

@@

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Spatially resolved dynamics at $z \sim 3.5$]{The KMOS Deep Survey: Resolved gas dynamics at $z \sim 3.5$}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[O.J. Turner et al.]{
Owen J. Turner,$^{1}$\thanks{E-mail: turner@roe.ac.uk (OJT)}
M. Cirasuolo,$^{1}$
J. Dunlop$^{1}$
R. J. McLure$^{1}$
\\
% List of institutions
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

@@

% Abstract of the paper
\begin{abstract}
We present first results from the KMOS Deep Survey (KDS), which is an ESO guaranteed time survey of 80 star-forming galaxies in the redshift range $z = 3 - 3.8$.
From this sample we detect spatially resolved [OIII5007] emission in the K-band from 57 galaxies, allowing us to explore the fraction which show ordered rotational motions, presumably in a star-forming disk.
41 galaxies show a clear, smooth velocity gradient along the kinematic axis, meriting them for further investigation via dynamical modelling.
The ratio of maximum rotational velocity to intrinsic velocity dispersion, $v / \sigma _{int}$, is commonly used to indicate the extent to which the gas in disk galaxies is dominated by ordered rotation or random motions.
We find that 16 galaxies have $v / \sigma _{int} > 1$, in broad agreement with results found at similar and low redshift.
The mean values of $v / \sigma _{int}$ are substantially lower in this redshift range than are observed locally; since the measured rotational velocity values have remained roughly constant over cosmic time this suggests that turbulent gas motions within the disk become steadily more important with increasing redshift.
We investigate the causes for this, linking the increase in $\sigma _{int}$ to increasing gas fraction and decreasing galaxy size, following the virial theorem and a $(1 + z)^{-1}$ scaling.
Finally we look into correlations between the maximum rotational velocity of galaxies and their global properties, finding that galaxies with higher stellar mass tend to rotate faster.

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
Integral Field Unit -- KMOS -- Dynamics -- Turbulence
\end{keywords}

@@

NO UNIVERSALLY DEFINED MEASURE OF THE CIRCULAR VELOCITY, OR THE POINT AT WHICH TO EXTRACT THAT VALUE.

% Check references here - exactly where does this scenario come from? 
In the hierarchical collapse scenario \citep{Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter haloes (Lifshitz 1960) \cite{Silk1968,Peebles1970}.
Mixed amongst this dark matter is baryonic gas, which is initially shock heated to the virial temperature of the halo during the gravitational collapse \citep{Birnboim2003,Keres2005,Dekel2006}.
As the baryons collectively cool, they accumulate at the centre of the potential well of the host halo as dense and cold protogalactic gas.
One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue.

It is an observationally determined fact that the galaxy population is bimodal in many physical properties at each epoch after galaxies begin to form, with a preference for the most massive galaxies to lie in the red sequence, characterised by red colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
\citep{Abramson2016,Abramson2016a}
\citep{Pannella2009a}

\citep{Baldry2006}
simulations explaining the biodality in terms of AGN feedback and a cut at a characteristic mass scale.
\citep{Birnboim2003,Dekel2006,Keres2005,Bower2006,Croton2006}
Explaining the observed number densities of early and late type galaxies at different epochs in terms of their formation mechanisms and evolutionary histories is one of the key goals of modern astronomy.
Two scenarii have emerged. The first highlights the importance of secular evolution, whereby cold gas accreted along cosmic web filaments `tops up' the existing baryon supply which fuels star formation, stellar mass within a galaxy is continually built up with in-situ star formation and the rate of star formation itself is regulated by both stellar and AGN feedback.
In this picture there is a certain mass scale above which a galaxy becomes quenched - EXPAND UPON THAT
The second suggests that environmental effects dominate the evolutionary demographic, with mass buildup predominantly occuring through minor mergers and major mergers triggering the cessation of star formation and building the red sequence at each epoch.  
Throughout the last few years both the results from simulations REF and observations have pushed the community towards the former picture, which downplays the significance of mergers in driving galaxy evolution.

%,Understanding the evolving dynamical state of disky star-forming galaxies (SFGs) throughout cosmic time is central to understanding the topics of galaxy formation and evolution.
%There are two different evolutionary scenarii.
%The first suggests that the buildup of stellar mass, $M_{*}$, over time within galaxies is hierarchical, with minor mergers steadily contributing to $M_{*}$ and major mergers bringing about the cessation of star formation by shock heating of the cold molecular gas. 
%The second is the equilibrium model of galaxy evolution e.g. \cite{Genel2008,Bouche2010,Dave2011,Dave2011a,Dave2011b,Krumholz2012,Lilly2013}, where the gas content of SFGs regulates their Star Formation Rates (SFRs) and varies smoothly inside individual galaxies throughout their lifetimes.
%In this picture the galactic gas budget is mediated by inflows of cold gas along cosmic web filaments \citep{Keres2005,Dekel2006} processing of the cold gas with steady, secular star formation and by outflows of gas from Active Galactic Nuclei (AGN) and stellar feedback.
%SFGs locked in this cycle of gas consumption form a galactic `Main Sequence', which is a fairly tight relationship between the SFR and stellar mass $M_{*}$  
%Over the last decade there have been considerable advancements

References for other things
MAIN SEQUENCE
\citep{Daddi2007} \citep{Elbaz2011a} \citep{Elbaz2007} \citep{Noeske2007a}

These are all the references for kinematics, not all the references for other things and other aspects of galaxy evolution. 
\citep{Wisnioski2015} \citep{ForsterSchreiber2009} \citep{ForsterSchreiber2006} \citep{Stott2016} \citep{Gnerucci2011} \citep{Epinat2012} ,\citep{Epinat2009} \citep{Epinat2010} \citep{Lilly2013} \citep{Saintonge2013} \citep{Wisnioski2011} \citep{Wright2007} \citep{Wright2009} \citep{Genzel2008} \citep{Genzel2006} \citep{Shapiro2008} \citep{Jones2010a} \citep{Newman2013} \citep{Genel2008} \citep{Nesvadba2008} \citep{Queyrel2012} \citep{Law2007} \citep{Law2009}
\citep{Simons2016} \citep{Pelliccia2016} \citep{Genzel2011} \citep{Epinat2008} \citep{Epinat2008a} \citep{Puech2008} \citep{Puech2007} \cite{Holmberg1958} \citep{Kassin2012} \citep{Flores2006} \citep{Neichel2008} \citep{Miller2011} \citep{Nesvadba2006} \citep{Nesvadba2007} \citep{Livermore2015} \citep{Swinbank2006} \citep{Swinbank2007} \citep{Swinbank2009} \citep{Cortese2014} \citep{VanderWel2012} \citep{Genzel2014a} \citep{Genzel2014} - for the PSF used when Galfitting F160W.

MOTIVATING THE FOLLOWING SECTION

The KMOS Deep Survey (KDS) is a guaranteed time programme focussing on the spatially resolved properties of star forming galaxies during a time where the universe is building to peak activity.
There are still many open questions which we can begin to answer by studying the emission, or lack thereof, from regions of ionised gas within individual galaxies at these redshifts.
For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
\textbf{(2)} What are the radial gradients in metal enrichment and would evidence for inverse gradients suggest infall of pristine gas to the central regions of these galaxies?
\textbf{(3)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?
\textbf{(4)} What role does formation environment play in shaping the dynamical and chemical evolution of galaxies? 
KMOS benefits from the ability to study many targets simultaneously, with 24 deployable IFUs patrolling a $7^{\prime}$ patch of sky.
Attempting to spatially resolve the flux from emission lines at $z \sim 3.5$ necessarily requires on source integration times $>$ 6 hours, and so the multiplexing capability provides KMOS with an enormous advantage in terms of observing time over other instruments for this type of study.
This has the knock-on effect of enabling a more general galaxy selection criteria, so that the KDS targets will be representative of the main sequence star forming population.

Many of these questions have already been addressed at lower redshift, as described above \citep{ForsterSchreiber2009,Wisnioski2015,Stott2016}, and also in a similar redshift range \cite{Gnerucci2011}.
The KDS will complement the lower redshift results by providing an additional data point on any plots showing evolutionary sequences of derived physical properties, therefore providing a more complete description of galaxy evolution starting from before cosmic high noon and running up to the present day.
The high redshift results of \cite{Gnerucci2011} will be expanded upon by the KDS, which extends to lower stellar masses and will increase the sample size for which physical properties can be resolved by roughly a factor of three.

In this paper we focus on deriving and interpreting the spatially resolved kinematics of KDS galaxies using the [OIII5007] emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$, and focussing on forming evolutionary links with lower redshift work.
We combine our KMOS data with the high resolution and sensitivity of the Hubble Space Telescope (HST) WFC3 H-band imaging in a spectro-photometric analysis, so that the kinematics can also be understood in the context of galaxy morphology.
In a future paper, (Turner \textit{et al.} in prep.), we will investigate the radial gradients in galaxy metallicity and hence the spatially resolved physical conditions within the ISM.

The structure of the current paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction.
In \cref{sec:extracting_properties} we explain how the two-dimensional maps of physical properties were extracted from our stacked datacubes and then describe the treatment of these maps and the modelling which leads to the final table of physical properties for the KDS galaxies. 
\cref{sec:results} presents our physical findings which are then discussed in \cref{sec:discussion}.
We then conclude in \cref{sec:conclusions}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY \& DATA REDUCTION}\label{sec:Survey_and_data}

% note going to assume here that the KMOS targets were selected from 
% from VVDS, COSMOS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notes for the sample selection plots
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. mstar vs sfr - must have full sample in the backgroud 
% and also lines showing where the main sequence of star formation
% should lie on this plot
% 2. colour vs mass plots - showing again the general population in 
% the background - will need to convert fluxes to magnitudes?
% Maybe a redshift vs. magnitude plot or something similar, showing
% how faint these targets are.

\subsection{The KMOS Deep Survey: sample selection and observations}
Our target selection for the KDS sample is designed to pick out star-forming galaxies at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
Within this redshift range the [OIII4959,5007] doublet and the $H_{beta}$ emission lines are visible in the K-band and the [OII3727,3729] doublet is visible in the H-band, both of which are observable with KMOS. 
We also want to draw galaxies covering a wide range in the SFR-$M_{*}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux. %FIGURE REFERENCE%
Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission, during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
These `Lyman-Alpha Blobs' (LABs), which are extended and diffuse emission regions associated with but not centred on LBGs \citep{Steidel2000}, and especially LAB01, have been the subject of much previous study, e.g. \citep{Bower2004a}, \citep{Matsuda2004,Matsuda2007}, \citep{Geach2006,Geach2014}, \citep{Weijmans2010}, \citep{Hayes2011a} and LAB01 was the study of a recent campaign \citep{Geach2016} using data from MUSE, \citep{Bacon2010}, ALMA, \citep{Wootten2009}, and MOSFIRE, \citep{McLean2012}.
These studies generally conclude that LABs are observed at the peaks of the cosmic density field and are therefore the progenitors of the most massive galaxy clusters, but the precise origin of the nebulous Ly$\alpha$ line emission is still unknown.

The non-cluster environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 imaging with $\sim 0.1^{\prime\prime}$ angular resolution, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII5007] or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (goodsp1) and north-west (goodsp2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).

% Add the programme ID for HST WFC3 imaging
The cluster galaxies are all from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003}, \citep{Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS, \citep{Shapley2003}, \citep{Nestor2013}, and when combined with deep B,V,R band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival HST ACS and WFC3 imaging covering large swathes of the field, the ancillary data is in excellent support of integral field spectroscopy.
Spectroscopic data quality assessment and OH feature avoidance criteria are applied in the same way as discussed above, and we fill the KMOS IFUs with galaxies in two pointings spanning the SSA22$\_$a (ssap1) and SSA22$\_$b (ssap2) fields.

>>>>

\documentclass[fleqn,usenatbib]{mn2e}

\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=cyan}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}

% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}   % Including figure files
\graphicspath{{Users/}{owenturner/}{Documents/}{PhD/}{KMOS/}{paper_1/}{Figures/}}
\usepackage{amsmath}    % Advanced maths commands
\usepackage{amssymb}    % Extra maths symbols
\usepackage[flushleft]{threeparttable}

@@

\newcommand{\Sers}{S\'{e}rsic }
\newcommand{\Lagr}{\mathcal{L}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%  PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[KDS: dynamical properties of z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
J. Dunlop,$^{1}$
R. J. McLure,$^{1}$\newauthor
A. M. Swinbank$^{4,3}$
H. L. Johnson$^{3,4}$
\\
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2017}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements of 44 O[III]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements push back the frontier of dynamical studies utilising Integral-Field Spectroscopy, and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$, and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
The mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with previous studies which have reported increasing $\sigma_{int}$ values with redshift.
We find that $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this evolution the result of the gradual size evolution of the star-forming population over cosmic time.
Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
To explore this further, we plot the S$_{0.5}$-stellar mass relation, finding that the slope and normalisation are consistent with measurements between $z=0-1.2$, however we caution that there is no clear connection between $\sigma_{int}$ and stellar mass.
These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
There is a very high merger fraction of 89\% in a pointing covering the centre of the $z\sim3.1$ protocluster in the SSA22-a field, and merger fraction of 15\% across the remaining pointings.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies:kinematics and dynamics -- galaxies:evolution -- galaxies:integral field spectroscopy
\end{keywords}

@@

In the hierarchical collapse scenario \citep{Rees1977,Fall1980}, matter density perturbations, which originate from some set of cosmological initial conditions, grow over time before condensing out of the general expansion to form dark matter halos \cite{Silk1968,Peebles1970}.
It is at the centre of these halos that baryons collect, cool and begin to form stars (\cite{Birnboim2003,Keres2005,Dekel2006} and see e.g. \cite{Mo2010} for a recent review), with these systems constituting the first galaxies.
One crucial ingredient shaping the subsequent evolution of this system is the transfer of angular momentum from the collapsing gas, as a protogalaxy which is rich in angular momentum is likely to form a turbulent, rotating disk, whereas if the angular momentum is low the formation of a spherical system dominated by random motions will ensue (e.g. \cite{Fall1983}).

It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied (e.g. as listed in \cite{Dekel2006}), with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, and outflows and accretion events maintain a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sparre2015,Lee2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic star formation rate density in this redshift range \citep{Madau_2014}.
At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b}, and also assumes that something can be learned about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
The picture is complicated by the addition of major and minor mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014}, and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010}.

Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations which must be reproduced across cosmic time.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons, and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \cite[e.g.][]{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Bundy2015,Wisnioski2015,Stott2016} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope (HST) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Harrison2016,Mason2016} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic Star Formation Rate Density (SFRD) \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
There is also an increasing body of work measuring the relationship between the observed maximum rotational velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Tiley2016a,Harrison2017}.
In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
\textbf{(4)} What are the connections between the chemical properties and the kinematics of the gas, particularly in terms of inflows and outflows of material?

This study focusses on the final question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotational velocities and velocity dispersions, using the [OIII]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to spatially resolve [OIII]$\lambda$5007 emission in 44 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$.

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:extracting_properties} we explain how two-dimensional maps of physical properties were extracted from our stacked datacubes and the treatment of the HST imaging to derive the morphological properties of our galaxies.
We also define a classification procedure which separates the KDS galaxies into a merger and modelling sample.
In \cref{sec:Kinematic_Properties} we present the kinematic modelling applied to the KDS galaxies, including the beam smearing correction, and the method chosen to extract the kinematic properties following this modelling procedure.
\cref{sec:results} presents an analysis of the derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY \& DATA REDUCTION}\label{sec:Survey_and_data}
\subsection{The KMOS Deep Survey: sample selection and observations}
Our target selection for the KDS sample is designed to pick out star-forming galaxies at $z = 3-4$, supported by deep multi-wavelength ancillary data and probing both cluster and field environments.
Within this redshift range the [OIII]$\lambda$4959,$\lambda$5007 doublet and the $H_{\beta}$ emission lines are visible in the K-band and the [OII$\lambda$3727,$\lambda$3729] doublet is visible in the H-band, both of which are observable with KMOS. 
We also want to draw galaxies covering a wide range in the SFR-$M_{\star}$ relation, so that we are ultimately tracking the physical properties of a representative sample of the star-forming population at these redshifts.
For these reasons, and to ensure a high detection rate of the ionised gas emission lines in the KDS galaxies, we select galaxies in well studied fields that have a previous spectroscopic detection.
To avoid biasing the sample towards blue and highly star-forming galaxies we make no secondary cuts on the basis of mass and flux. %FIGURE REFERENCE%
Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in SSA22 were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
These `Lyman-Alpha Blobs' (LABs), which are extended and diffuse emission regions associated with but not centred on LBGs \citep{Steidel2000}, and especially LAB01, have been the subject of much previous study, e.g. \citep{Bower2004a}, \citep{Matsuda2004,Matsuda2007}, \citep{Geach2006,Geach2014}, \citep{Weijmans2010}, \citep{Hayes2011a} and LAB01 was the study of a recent campaign \citep{Geach2016} using data from MUSE, \citep{Bacon2010}, ALMA, \citep{Wootten2009}, and MOSFIRE, \citep{McLean2012}.
These studies generally conclude that LABs are observed at the peaks of the cosmic density field and are therefore the progenitors of the most massive galaxy clusters, but the precise origin of the nebulous Ly$\alpha$ line emission is still unknown.

The low-density environment galaxies are selected from the GOODS-S field, accessible from the VLT and with excellent multi-wavelength coverage, including deep HST WFC3 F160W imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [OIII]$\lambda$5007 or H$_{\beta}$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions of spatial overdensity in the south-east (GOODS-S-P1) and north-west (GOODS-S-P2) to fill the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
% Add the programme ID for HST WFC3 imaging
The cluster galaxies are selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an extreme overdensity of LBG candidates at $z \sim 3.09$.
